Galois Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis

### 2014-11-13 writeup/pldi15.tex

\par Significantly, a Galois transformer can be proved sound once and
for all, making it a reusable analysis component.  As new analysis
features and abstractions are developed and mixed in, soundness proofs
need not be reconstructed as the composition of a monad transformer
stack is sound by virtue of its constituents.  We believe Galois
transformers provide a viable foundation for reusable and composable 
metatheory for program analysis.
\end{abstract}
% }-}

>>>>

\par Significantly, a Galois transformer can be proved sound once and
for all, making it a reusable analysis component.  As new analysis
features and abstractions are developed and mixed in, soundness proofs
need not be reconstructed, as the composition of a monad transfomer
stack is sound by virtue of its consituents.  We believe Galois
transformers provide a viable foundation for resuable and composable 
metatheory for program analysis.
\end{abstract}
% }-}
